M.Sc. Proposal

### 2010-09-26 notes/proposal.tex
Fix proposal.

After the iterations have converged to a solution for the coupled
system, the total stress tensor $\mathbb{T}$ on the particle
$\cl{S} = \left\{\bx : \|\bx\| = 1\right\}$ is computed
(\ref{eq:Stress}) and integrated to yield the total force
(\ref{eq:Force}):
\begin{eqnarray}
  \label{eq:Stress}
  \mathbb{T} &=& - P \mathbb{I} + \bnabla \bV + (\bnabla \bV) ^T  +
  \bnabla \varPhi \bnabla \varPhi - \frac{\bnabla \varPhi \cdot \bnabla \varPhi}{2} \mathbb{I}, \\
  \label{eq:Force}
  \vect{F} &=& \int_{\cl{S}} \left(\mathbb{T} \cdot \bnhat \right) ds = \boldsymbol{0}.
\end{eqnarray}
Because the problem is axisymmetric, the force should be aligned
with the symmetry axis: $\vect{F} = F \bzhat$. Moreover, since the
particle is stress-free in steady flow, we have $F = 0$ for
steady-state velocity $\cl{U}$. This observation enables us to
find the correct $\cl{U}$ for given $\beta$, using a
one-dimensional root-finding algorithm on $F_\beta(\cl{U})$, as a
function of $\cl{U}$.

>>>>

After the iterations have converged to a solution for the coupled
system, the total stress tensor $\mathbb{T}$ on the particle
$\cl{S} = \left\{\bx : \|\bx\| = 1\right\}$ is computed
(\ref{eq:Stress}) and integrated to yield the total force
(\ref{eq:Force}):
\begin{eqnarray}
  \label{eq:Stress}
  \mathbb{T} &=& - P \mathbb{I} + \bnabla \bV + (\bnabla \bV) ^T  +
  \bnabla \varPhi \bnabla \varPhi - \frac{\bnabla \varPhi \cdot \bnabla \varPhi}{2} \mathbb{I}, \\
  \label{eq:Force}
  \vect{F} &=& \int_{\cl{S}} \left(\mathbb{T} \cdot \bnhat \right) ds = \boldsymbol{0}.
\end{eqnarray}
Because the problem is axisymmetric, the force should be aligned
with the symmetry axis: $\vect{F} = F \bzhat$. Moreover, since the
particle is stress-free in steady flow, we have $F = 0$ for
steady-state velocity $\cl{U}$. This observation enables us to
find the correct $\cl{U}$ for given $\beta$, using a
one-dimensional root-finding algorithm (e.g. the secant method) 
on $F_\beta(\cl{U})$, as a function of $\cl{U}$.
